A robust and memory-efficient transition state search method for complex energy landscapes

### 2022-08-28 manuscript.tex
Citations for hybrid string methods and studies comparing double ended methods.

Here we compare the speeds of convergence of BITSS to two often-used chain-of-states methods for finding transition states: climbing-image nudged elastic band (CINEB) \cite{Henkelman2000a}, and DNEB with hybrid eigenvector following (DNEB-HEVF) \cite{Cerjan1981}.
It is also possible to use hybrid methods based upon the string method, although the results are expected to be similar.
Further, here we aim to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the available methods.

>>>>

Here we compare the speeds of convergence of BITSS to two often-used chain-of-states methods for finding transition states: climbing-image nudged elastic band (CINEB) \cite{Henkelman2000a}, and DNEB with hybrid eigenvector following (DNEB-HEVF) \cite{Cerjan1981}.
It is also possible to use hybrid methods based upon the string method \cite{E2007,Zimmerman2013}, although the results are expected to be similar.
Also, we primarily aim to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the available methods, which has been performed in other works \cite{Koslover2007,Sheppard2008}.
